Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-12 soundness.tex
+

As a last definition, we give the head step relation required for the Iris instantiation for our simple language in Figure \ref{} to sequence instructions. This relation allows lifting the program expression to enable the application of changes imposed by the operational semantics on the program state (for a certain cpu, a register map, and a selected memory for an address-space) when applied for an insturction (\textsf{i}).
\begin{lstlisting}[language=Coq]
Definition exec_step (i: instr) ($\sigma$:state) : option state :=
    exec_instr i $\sigma\mathcal{C}$ $\sigma.\mathcal{R}$ ((memToPhysMem $\sigma.\mathcal{M}$)  ($\sigma.\mathcal{R}$ !!  cr3)).
\end{lstlisting}
\todo[inline,color=yellow]{Colin, in case needed,not proven, could you simply say that we assume these map equalities or a paper proof etc.}. Again, due to the page limits, we can only give an outline of proof for a selected instruction (\TirNameStyle{WriteToRegFromVirtMem}) from our \textsf{AMD64} model. However, mechanized soundness proofs of other instructions can be found as a part of our submission artifact.

>>>>

As a last definition, we give the head step relation required for the Iris instantiation for our simple language in Figure \ref{} to sequence instructions. This relation allows lifting the program expression to enable the application of changes imposed by the operational semantics on the program state (for a certain cpu, a register map, and a selected memory for an address-space) when applied for an insturction (\textsf{i}).
\begin{lstlisting}[language=Coq]
Definition exec_step (i: instr) ($\sigma$:state) : option state :=  exec_instr i $\sigma.\mathcal{C}$ $\sigma.\mathcal{R}$ ((memToPhysMem $\sigma.\mathcal{M}$)  ($\sigma.\mathcal{R}$ !! cr3)).
\end{lstlisting}
\todo[inline,color=yellow]{Colin, in case needed,not proven, could you simply say that we assume these map equalities or a paper proof etc.}. Again, due to the page limits, we can only give an outline of proof for a selected instruction (\TirNameStyle{WriteToRegFromVirtMem}) from our \textsf{AMD64} model. However, mechanized soundness proofs of other instructions can be found as a part of our submission artifact.
